\chapter*{About this book}

The active inference literature presents numerous equations used for modeling action and perception in continuous and discrete state-spaces. However, the proofs of these equations are either scattered in the literature (usually in supplemental material) or left as an exercise for the reader. The equations in the literature often use very different notational conventions making it difficult to make connections to other equations in the literature.

While preparing \textit{Fundamentals of Active Inference}, the author (Sanjeev Namjoshi) derived many of these equations and consolidated those found in other papers and supplemental materials.\footnote{The vast majority of equations in \textit{Fundamentals of Active Inference} are available in this text. The remaining proofs, largely for equations that are related to more conventional statistics or machine learning concepts, are presented in full on the author's website: \url{https://www.sanjeevnamjoshi.com/faif/proofs}.} This book gathers all of these equations to provide a single compendium of proofs for every equation in the literature. This work was heavily edited and greatly improved by the work of Fraser Patterson who ensured the proofs were easy to follow and sound.

As this text is intended to serve as more of a reference than a textbook the reader is assumed to have basic familiarity with the active inference literature. Nevertheless, an overview of the basics is presented in the first chapter to orient the reader. The notational conventions are described in detail in the appendix.
